### 2023-07-18 README.Rmd
add tests and fix packages

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

devtools::load_all()
```

@@

@@

```{r, echo = FALSE, message=FALSE, warning=FALSE, results='asis'}
pkgs <- get_packages()
sprintf("- `%s` (%s)", pkgs$pkg, pkgs$version) |> 
  cat(sep = "\n")
```

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE,
  warning = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

devtools::load_all()
pkgs <- simulatingMeta:::.get_packages()
```

@@

## Testing

The custom functions are tested within the `scripts/test.R` script. The idea is to use the same simulation codes of the paper increasing the $k$ and $n$ values and check the recovery of simulated parameters using the `check_sim()` function.

@@

```{r, echo = FALSE, message=FALSE, warning=FALSE, results='asis'}
sprintf("- `%s` (%s)", pkgs$pkg, pkgs$version) |> 
  cat(sep = "\n")
```
